Undecidability and the structure of the Turing degrees

### 2018-08-16 paper.tex
Cleaning up Senizergues, further reading sections

The decidability of the following problem was an open problem in the field of
computability theory from 1965, when it was introduced by Ginsburg and Greibach \cite{ginsburg65:_deter}. In 1997, when it was solved by G\'eraud S\'enizergues
\cite{senizergues_det_pd_decid}. A sketch of the proof follows.

\begin{prob}[The Equivalence Problem for Deterministic CFGs]
  Let $L_1,L_2$ be deterministic context-free languages. Is $L_1=L_2$?
\todo{}
\end{prob}

@@

\section{Further Reading}
The study of the Turing degrees was a very active topic in the late
20\textsuperscript{th} and early 21\textsuperscript{st} centuries, and this
paper has just scratched the surface of the field. \par
Readers particularly interested in the structure of the computably enumerable
degrees might be interested in a result by Sacks in 1964 showing their
density~\cite{sacks64:_recur_enumer_degrees_dense}, while those interested in
\aclp{CFG} or the Turing degrees of problems about them should consult \cite{REEDY197577} and
\cite{ginsburg66:_mathem_theor_contex_languag}
\cite{hopcroft07:_introd_autom_theor_languag_comput}\todo{chapter for cfgs}. For excellent, comprehensive,
and more rigorous textbooks on the study of Turing computability and the Turing
degrees, consider \cite{soare16_turin_comput} \cite{lerman16:_degrees_unsol} or
the classic text \cite{kleene80_introd}.

>>>>

Finally, the decidability of the equality problem for \acp{DCFL} was an open problem in the field of
computability theory from 1965, when it was introduced by Ginsburg and Greibach
until 1997, when it was shown to be decidable by G\'eraud S\'enizergues
\cite{ginsburg65:_deter,senizergues_det_pd_decid}. S\'enizergues received the 2002 G\"odel Prize
for the result.

@@

\section{Further Reading}
The study of the Turing degrees was a very active topic in the late
20\textsuperscript{th} and early 21\textsuperscript{st} centuries, and this
paper has just scratched the surface of the field. \par
Readers particularly interested in the structure of the computably enumerable
degrees might be interested in a result by Sacks in 1964 showing their
density~\cite{sacks64:_recur_enumer_degrees_dense}, while those interested in
\aclp{CFG} or the Turing degrees of problems about them should consult Reedy's
1975 paper on the Turing degree of a specific problem~\cite{REEDY197577} and
Ginsburg's book \emph{The Mathematical Theory of Context Free
  Languages}~\cite{ginsburg66:_mathem_theor_contex_languag}. Additionally, a
simple overview of the field is available in Hopcroft's classic text on
computability
theory~\cite[chs.~5--7]{hopcroft07:_introd_autom_theor_languag_comput}. \par For excellent, comprehensive,
and more rigorous textbooks on the study of Turing computability and the Turing
degrees, consider Soare and Lerman's
books~\cite{soare16_turin_comput,lerman16:_degrees_unsol}, as well as
Kleene's original text on the subject~\cite{kleene80_introd}.
